### 2015-12-24 extended-abstract.tex
half introduce model, but not sure where to explain uncertainty

Set up model
\begin{itemize}
	\item Take trade agreement tariff as given ($\tau^a_i$)
	\item Lobby exerts effort to convince ITC to apply anti-dumping duties (AD determined endogenously); there is a given amount of uncertainty for each $i$
	\item Given that lobby gets an ITC measure in first round of game and it stay stays in place, there is another round five years later; at this point, $\tau^{AD}$ is given
	\item Lobby decides how much effort to put forth given $\tau^{a}$, $\tau^{AD}$, $\ta$
\end{itemize}

@@

\vskip.3in
Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
			\item Need uncertainty, asymmetric information, something
			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
				\begin{itemize}
					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
					\item Does Congressional uncertainty transfer over to ITC uncertainty?
				\end{itemize}
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years)
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years?
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
	\item Also have to adapt model to cross-industry to get necessary variation
		\begin{itemize}
			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
		\end{itemize}
\end{itemize}

>>>>

In many countries, the crucial actors in the imposition of TTBs are advocates for the industry that would be protected and an administrative body that has been granted authority to make decisions about whether a given TTB is WTO-legal. In the United States, this body is the International Trade Commission (ITC). For ease of exposition and because I would ultimately like to test this theory using U.S. data, I will refer to the actors in this model as lobbies and the ITC. \\

In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, all the actors take most-favored-nation (MFN) tariffs as given. In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product. The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier. Importantly, we assume that this decision is not deterministic, with the amount of uncertainty varying by industry.

\begin{itemize}
	\item Given that lobby gets an ITC measure in first round of game and it stay stays in place, there is another round five years later; at this point, $\tau^{AD}$ is given
	\item Lobby decides how much effort to put forth given $\tau^{a}$, $\tau^{AD}$, $\ta$
\end{itemize}

@@

\vskip.3in
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
			\item Need uncertainty, asymmetric information, something
			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
				\begin{itemize}
					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
					\item Does Congressional uncertainty transfer over to ITC uncertainty?
				\end{itemize}
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years)
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years?
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
	\item Also have to adapt model to cross-industry to get necessary variation
		\begin{itemize}
			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
		\end{itemize}
\end{itemize}
